---
title: "Week 6- Linear Regression"
author: "Anna Zauner"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)

```

## Example of a rank-based test

We'll make our own samples, using a pseudorandom generator.

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)

```

```{r}
hist(gp_1)

hist(gp_2)

```
Try a t-test

```{r}
t.test(gp_1, gp_2)
```

What is the meaning of this p-value? p-value- 0.1982

If the two sample were taken from populations with the same mean, then there is a 19.8% chance that we would have found the means are at least as different as those selected in random samples. This is likely to occur therefore you can accept the null hypotheses. 

Alison's words: If these samples were drawn from population with the same mean, the probability of taking two random samples with means *at least as different* as the sample means we found by random chance (taking into account spread, n) is 19.8%

Retain (fail to reject) the null hypothesis. == there is no significant difference in means between group 1 and 2. Warning: people get weirdly upset if you say accept the null

Now let's compare this outcome to a rank-based test.

## Mann Whitney U unpaired rank-based test

```{r}
mwu <- wilcox.test(gp_1, gp_2)

mwu

```


If these samples came from populations with the same ranks (medians), then there is a 28% chance that randomly selected samples would have ranks at least as different as those in our samples. This is likely therefore we can retain the null hypothesis. There is no significant differences in the ranks between group 1 and group 2 (statistical summary) (Mann Whitney U test: U(df)= 86, p=0.28).

**make sure when picking which test to use, aligns with what saying to audience** (use same responsible metric-conistent message- either mean or median and stick with it)

## Linear Regression

Simple linear regression (single dependent variable, a single independent variable)

```{r, include=FALSE}
ggplot(data = penguins, aes(x= flipper_length_mm, y= body_mass_g))+
  geom_point()+
  geom_smooth(method = "lm")
```



Find a linear regression model using ordinary least squares describing the relationship between fliper length ans body mass for penguins.

3 pieces:
-What type of model?
-What is the relationship to model (DV ~ IV(s)
-Where is the data that's used to create this model?

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)

```

y = mx + b

y- body mass, x - flipper length, 

bodymass = 49.7(flipperlength) + -5780.8

49.7(g/mm) means - slope that relates flipper length to body mass, on average for every one mm increase in flipper length I expect a 49.7 increase in grams in body mass. 

-5780.8 (g) means if penguin had flipper length at zero, then body mass would be -5780.8 grams.


### broom packae returns model outputs as tidy data frames

```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm)

penguin_lm_tidy

broom::glance(penguin_lm) # talk about these things more on Wednesday

```

How can I actually include my model equation in a report?

```{r}
extract_eq(model = penguin_lm, use_coefs = TRUE) #produces pretty version of equation
```

```{r}
plot(penguin_lm)
```

