---
title: "Week 6- Linear Regression"
author: "Anna Zauner"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)

```

## Example of a rank-based test

We'll make our own samples, using a pseudorandom generator.

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)

```

```{r}
hist(gp_1)

hist(gp_2)

```
Try a t-test

```{r}
t.test(gp_1, gp_2)
```

What is the meaning of this p-value? p-value- 0.1982

If the two sample were taken from populations with the same mean, then there is a 19.8% chance that we would have found the means are at least as different as those selected in random samples. This is likely to occur therefore you can accept the null hypotheses. 

Alison's words: If these samples were drawn from population with the same mean, the probability of taking two random samples with means *at least as different* as the sample means we found by random chance (taking into account spread, n) is 19.8%

Retain (fail to reject) the null hypothesis. == there is no significant difference in means between group 1 and 2. Warning: people get weirdly upset if you say accept the null

Now let's compare this outcome to a rank-based test.

## Mann Whitney U unpaired rank-based test

```{r}
mwu <- wilcox.test(gp_1, gp_2)

mwu

```


If these samples came from populations with the same ranks (medians), then there is a 28% chance that randomly selected samples would have ranks at least as different as those in our samples. This is likely therefore we can retain the null hypothesis. There is no significant differences in the ranks between group 1 and group 2 (statistical summary) (Mann Whitney U test: U(df)= 86, p=0.28).



